---
title: "Who Wrote It? Identifying LLMs from Their Responses"
subtitle: "Penn State CMPSC 448: Midterm Project 1 Research Report"
author: "Blake Naluai"
date: "9 October 2026"
date-format: full
format:
  pdf:
    documentclass: article
    fig-pos: 'H'
    geometry: "top=1in,bottom=1in,left=1in,right=1in"
    #colorlinks: true
    toc: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| label: setup
#| include: false

# Load required packages
if (!requireNamespace("tidyverse", quietly = TRUE)) install.packages("tidyverse")
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")
if (!requireNamespace("knitr", quietly = TRUE)) install.packages("knitr")
if (!requireNamespace("gridExtra", quietly = TRUE)) install.packages("gridExtra")

library(tidyverse)
library(ggplot2)
library(knitr)
library(gridExtra)

# Set custom ggplot2 theme
theme_set(theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14, color = "#1a252f"),
    plot.subtitle = element_text(size = 11, color = "#576574"),
    axis.title = element_text(face = "bold", size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  ))

# Define palette
llm_colors <- c(
  "Anthropic (Claude)" = "#d9534f",
  "Meta (Llama)"       = "#337ab7",
  "OpenAI (GPT)"       = "#5cb85c"
)
```

{{< pagebreak >}}

# Executive Summary

This report investigates the challenge of **LLM Fingerprinting**: predicting which specific Large Language Model generated a given textual response. Using a curated dataset of $N=1,500$ interactions from the LMSYS Chatbot Arena across three major model families (**Anthropic Claude**, **Meta Llama**, and **OpenAI GPT**), we implement and compare two deep learning architectures in PyTorch: a 1D Multi-Kernel Convolutional Neural Network (**TextCNN**) and a Bidirectional Long Short-Term Memory network (**BiLSTM**).

Our empirical findings demonstrate:

1. **TextCNN outperforms BiLSTM on output classification**: TextCNN achieved **63.33% test accuracy** (Macro $F_1 = 0.64$) compared to BiLSTM's **56.67%** (Macro $F_1 = 0.57$), indicating that local n-gram stylistic markers are more predictive than long-range sequential dependencies.
2. **Response text provides primary signal**: Classifying based on user prompts alone yields **51.67% accuracy** (above 33.3% random baseline due to dataset prompt biases), but output responses remain the dominant fingerprint signal.
3. **Cross-Domain Generalization**: Models trained exclusively on non-coding tasks achieved **55.47% accuracy** when tested on unseen coding prompts, with Claude displaying a remarkably high recall of **0.95**.
4. **Linguistic Stylometry**: Quantitative feature extraction reveals distinct family traits—Claude produces substantially longer responses ($\mu = 1,075$ chars, 1.88 bullets/response) with lower Type-Token Ratio ($0.651$), whereas GPT and Llama generate concise answers with higher vocabulary diversity ($0.732$ and $0.712$).

{{< pagebreak >}}

# Section 1: Problem Definition & Dataset Curation

## 1.1 Problem Formulation

The task of LLM Fingerprinting is formulated as a multi-class text classification problem. Given an input context tuple $X = (x_{\text{prompt}}, x_{\text{output}})$, our objective is to learn a mapping $f: X \to Y$, where $Y \in \{\text{Anthropic (Claude)}, \text{Meta (Llama)}, \text{OpenAI (GPT)}\}$.

The target distribution is strictly balanced with $N = 1,500$ total records (500 per family) sampled from the `agie-ai/lmsys-chatbot_arena_conversations` dataset.

```{r dataset-summary}
#| label: tbl-dataset
#| tbl-cap: "Summary of Curated Dataset Distribution across LLM Families"

dataset_df <- data.frame(
  LLM_Family = c("Anthropic (Claude)", "Meta (Llama)", "OpenAI (GPT)"),
  Total_Samples = c(500, 500, 500),
  Train_Samples = c(400, 400, 400),
  Test_Samples = c(100, 100, 100),
  Representative_Models = c("Claude-2.1, Claude-Instant", "Llama-2-70b-chat, Vicuna-13b", "GPT-4-0613, GPT-3.5-Turbo")
)

knitr::kable(dataset_df, col.names = c("LLM Family", "Total", "Train (80%)", "Test (20%)", "Representative Variants"))
```

## 1.2 Text Preprocessing & Vocabulary Building

Text processing is performed via a custom vocabulary pipeline:

1. **Lowercasing & Cleaning**: Non-alphanumeric characters are stripped via regular expressions `[^a-z0-9\s]`.
2. **Frequency Vocabulary Construction**: A fixed vocabulary $V$ of top $10,000$ most frequent tokens is constructed, reserving indices `0` for `<PAD>` and `1` for `<UNK>`.
3. **Sequence Truncation & Padding**: Sequences are mapped to index arrays bounded by maximum sequence length $L = 256$.

$$x_{\text{encoded}} = [w_1, w_2, \dots, w_k, \text{PAD}, \dots, \text{PAD}], \quad k \le 256$$

{{< pagebreak >}}

# Section 2: Model Architecture & Training Details

## 2.1 TextCNN Architecture

The 1D TextCNN captures local $n$-gram features using three parallel 2D convolutional filter banks operating over token embeddings:

- **Embedding Layer**: $E \in \mathbb{R}^{|V| \times d}$, where embedding dimension $d = 128$.
- **Convolutional Feature Maps**: Parallel filters with sizes $k \in \{3, 4, 5\}$, each with $h = 100$ filters.
- **Pooling & Dropout**: Max-over-time pooling squeezes sequence features into fixed 100-dim vectors, concatenated into a 300-dim vector, followed by Dropout ($p = 0.3$).
- **Linear Classifier**: Fully connected layer mapping $\mathbb{R}^{300} \to \mathbb{R}^3$.

$$\mathbf{c}_k = \text{ReLU}(\text{Conv1d}(\mathbf{E}(x), k)), \quad \hat{\mathbf{c}}_k = \max(\mathbf{c}_k), \quad \mathbf{y} = \text{FC}(\text{Concat}(\hat{\mathbf{c}}_3, \hat{\mathbf{c}}_4, \hat{\mathbf{c}}_5))$$

## 2.2 TextRNN (BiLSTM) Architecture

The TextRNN leverages a 2-layer Bidirectional Long Short-Term Memory (BiLSTM) network to model temporal token dependencies:

- **Hidden State Dimension**: $h = 128$ per direction (256 combined).
- **Dropout**: $p = 0.3$ between LSTM layers and classification head.
- **Sequence Representation**: Concatenation of the final forward $\overrightarrow{h}_T$ and backward $\overleftarrow{h}_1$ hidden states.

$$\mathbf{h}_{\text{out}} = [\overrightarrow{h}_T \parallel \overleftarrow{h}_1] \in \mathbb{R}^{256}, \quad \mathbf{y} = \text{FC}(\text{Dropout}(\mathbf{h}_{\text{out}}))$$

## 2.3 Training Parameters

Both networks were trained using Cross-Entropy Loss and the Adam optimizer:

- **Learning Rate**: $\eta = 0.001$
- **Batch Size**: $32$
- **Epochs**: $5$
- **Loss Function**: $\mathcal{L} = -\sum_{i=1}^3 y_i \log(\hat{y}_i)$

{{< pagebreak >}}

# Section 3: Experimental Results (RQ1)

## 3.1 Model Comparison: CNN vs. BiLSTM

**Research Question 1**: *Can deep neural networks identify the generating LLM from output text alone, and how do CNNs compare to RNNs?*

When trained exclusively on model generated responses (`output_only`), the **1D TextCNN** achieved a test classification accuracy of **63.33%** (Macro $F_1$: **0.64**), outperforming the **Bidirectional TextRNN (BiLSTM)**, which achieved **56.67%** accuracy (Macro $F_1$: **0.57**). Both models significantly exceeded the 33.33% baseline of random guessing across a 3-class balanced dataset ($N=1,500$, $n=500$ per class).

```{r rq1-results-table}
#| label: tbl-rq1
#| tbl-cap: "Classification Performance on Test Set (Output Only, N=300)"

rq1_perf <- data.frame(
  Model = c("TextCNN", "TextCNN", "TextCNN", "TextCNN (Overall)",
            "TextRNN (BiLSTM)", "TextRNN (BiLSTM)", "TextRNN (BiLSTM)", "TextRNN (Overall)"),
  LLM_Family = c("Anthropic (Claude)", "Meta (Llama)", "OpenAI (GPT)", "Macro Average / Accuracy",
                 "Anthropic (Claude)", "Meta (Llama)", "OpenAI (GPT)", "Macro Average / Accuracy"),
  Precision = c(0.85, 0.54, 0.61, 0.67, 0.63, 0.55, 0.52, 0.57),
  Recall = c(0.56, 0.75, 0.59, 0.63, 0.66, 0.48, 0.56, 0.57),
  F1_Score = c(0.67, 0.63, 0.60, 0.64, 0.64, 0.51, 0.54, 0.57),
  Accuracy = c(NA, NA, NA, 0.6333, NA, NA, NA, 0.5667)
)

knitr::kable(rq1_perf, col.names = c("Model Architecture", "Class / Metric", "Precision", "Recall", "F1-Score", "Overall Accuracy"))
```

```{r rq1-performance-chart}
#| label: fig-rq1-chart
#| fig-cap: "Comparison of Precision, Recall, and F1-Score across LLM Families for TextCNN vs. BiLSTM"

perf_long <- rq1_perf %>%
  filter(!grepl("Overall", LLM_Family)) %>%
  pivot_longer(cols = c("Precision", "Recall", "F1_Score"), names_to = "Metric", values_to = "Value")

ggplot(perf_long, aes(x = LLM_Family, y = Value, fill = Model)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  facet_wrap(~ Metric) +
  scale_fill_manual(values = c("TextCNN" = "#2c3e50", "TextRNN (BiLSTM)" = "#e74c3c")) +
  scale_y_continuous(limits = c(0, 1.0), labels = scales::percent) +
  labs(title = "RQ1: Classification Performance by Model Architecture",
       y = "Score", x = "") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

{{< pagebreak >}}

## 3.2 Class-Level Dynamics & Confusion Matrix Analysis

Analyzing confusion matrices reveals key class-level prediction dynamics and architectural trade-offs:

```{r rq1-confusion-matrices}
#| label: fig-rq1-cm
#| fig-cap: "Confusion Matrices for TextCNN and TextRNN on Output-Only Classification"

cm_cnn <- data.frame(
  Actual = factor(rep(c("Anthropic", "Meta", "OpenAI"), each = 3), levels = c("Anthropic", "Meta", "OpenAI")),
  Predicted = factor(rep(c("Anthropic", "Meta", "OpenAI"), 3), levels = c("Anthropic", "Meta", "OpenAI")),
  Count = c(56, 28, 16, 4, 75, 21, 6, 35, 59)
)

cm_rnn <- data.frame(
  Actual = factor(rep(c("Anthropic", "Meta", "OpenAI"), each = 3), levels = c("Anthropic", "Meta", "OpenAI")),
  Predicted = factor(rep(c("Anthropic", "Meta", "OpenAI"), 3), levels = c("Anthropic", "Meta", "OpenAI")),
  Count = c(66, 16, 18, 19, 48, 33, 20, 24, 56)
)

p1 <- ggplot(cm_cnn, aes(x = Predicted, y = Actual, fill = Count)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = Count), fontface = "bold", color = "white", size = 5) +
  scale_fill_gradient(low = "#34495e", high = "#16a085") +
  labs(title = "TextCNN Confusion Matrix", subtitle = "Test Accuracy: 63.33%") +
  theme(legend.position = "none")

p2 <- ggplot(cm_rnn, aes(x = Predicted, y = Actual, fill = Count)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = Count), fontface = "bold", color = "white", size = 5) +
  scale_fill_gradient(low = "#34495e", high = "#e67e22") +
  labs(title = "BiLSTM Confusion Matrix", subtitle = "Test Accuracy: 56.67%") +
  theme(legend.position = "none")

grid.arrange(p1, p2, ncol = 2)
```

### Class-Specific Observations:
- **Anthropic (Claude)**: In the TextCNN, Claude achieved the highest precision (**0.85**). Out of 100 actual test instances, 56 were correctly identified, 28 were misclassified as Llama, and 16 as GPT. In the BiLSTM, Claude achieved a more balanced precision of **0.63** and recall of **0.66** (66/100 correct).
- **Meta (Llama)**: The TextCNN demonstrated high recall for Llama (**0.75**; 75/100 correct). However, its precision dropped to **0.54** because 35 GPT responses and 28 Claude responses were incorrectly predicted as Llama.
- **OpenAI (GPT)**: The TextCNN achieved a balanced precision of **0.61** and recall of **0.59** (59/100 correct). In contrast, BiLSTM misclassified 20 GPT instances as Claude and 24 as Llama, yielding a lower $F_1$-score of **0.54**.

## 3.3 Architectural & Theoretical Deep Dive

1. **Local N-Gram Feature Extraction (TextCNN)**: The TextCNN utilizes 1D convolutional filters of sizes $k \in \{3, 4, 5\}$ ($100$ filters per kernel size). These filters act as parallel n-gram detectors that slide over embedding channels ($d=128$). Coupled with **Max-Over-Time Pooling**, the CNN extracts the single strongest activation for each feature map across the sequence. Stylistic "fingerprints"—such as bullet point syntax (`- `), markdown header notation (`**`), or specific transition phrases—trigger high activation values regardless of where they appear in the response.
2. **Sequential Context vs. Noise Sensitivity (BiLSTM)**: The BiLSTM processes text sequentially, updating hidden states $h_t = f_W(h_{t-1}, x_t)$ across time steps. While gating mechanisms ($\\mathbf{i}_t, \mathbf{f}_t, \mathbf{o}_t$) mitigate vanishing gradients, propagating hidden vectors across fixed sequence lengths ($L=256$) forces the model to encode global word order. Because stylistic LLM signatures are locally concentrated rather than structurally sequential, global temporal pooling in BiLSTMs introduces sequence-level noise, leading to higher validation loss (**1.2250** vs. CNN's **0.8397**) and lower accuracy.

{{< pagebreak >}}

# Section 4: In-Depth Research Analyses

## 4.1 RQ2: Role of the User Prompt (Input Context)

**Research Question 2**: *How does classifier performance change when trained on Input Only vs. Output Only vs. Input + Output concatenated?*

```{r rq2-input-mode-chart}
#| label: fig-rq2-chart
#| fig-cap: "Accuracy & Macro F1 Score Across Input Modes (TextCNN)"

rq2_data <- data.frame(
  Input_Mode = c("Input Only (Prompt)", "Output Only (Response)", "Input + Output Concatenated"),
  Accuracy = c(0.5167, 0.6333, 0.6133),
  Macro_F1 = c(0.5200, 0.6400, 0.6000)
)

rq2_long <- rq2_data %>%
  pivot_longer(cols = c("Accuracy", "Macro_F1"), names_to = "Metric", values_to = "Score")

ggplot(rq2_long, aes(x = Input_Mode, y = Score, fill = Metric)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.6) +
  scale_fill_manual(values = c("Accuracy" = "#2980b9", "Macro_F1" = "#8e44ad")) +
  scale_y_continuous(limits = c(0, 0.8), labels = scales::percent) +
  geom_text(aes(label = sprintf("%.1f%%", Score * 100)), position = position_dodge(width = 0.7), vjust = -0.5, size = 3.5) +
  labs(title = "RQ2: Impact of Input Mode on Classification Performance", x = "", y = "Score")
```

### In-Depth Interpretation & Prompt Distribution Bias:
1. **Prompt-Only Predictability (51.67%)**: Classifying LLM identities from user prompts alone yielded an accuracy over 18% higher than random chance ($33.3\%$). This occurs due to **prompt selection bias** inherent in crowd-sourced datasets like LMSYS Chatbot Arena. Users intentionally select specific models for complex domain tasks—submitting advanced coding, mathematics, or philosophical queries to models like Claude or GPT-4, while using lighter models for brief factual queries. The classifier learns these prompt distribution patterns rather than an intrinsic model property.
2. **Output Only (63.33%)**: Response text remains the single best predictor of model origin.
3. **Noise Contamination in Concatenation (61.33%)**: Concatenating `LLM_Input` with `LLM_output` slightly decreased overall accuracy compared to `output_only` (61.33% vs. 63.33%). Because input sequences are truncated at $L=256$ tokens, prepending prompt tokens consumes sequence budget, truncating the trailing portion of the LLM response where key formatting markers and conclusions reside. However, concatenation reduced validation loss to **0.8000** (vs. 0.8397 for output-only), indicating higher model confidence on correctly predicted instances due to dual-context signals.

---

## 4.2 RQ3: Cross-Domain Generalization

**Research Question 3**: *Can a model trained on general QA and creative writing generalize to identify LLMs on unseen coding tasks?*

- **Training Set**: $1,363$ non-coding interactions.
- **Evaluation Set**: $137$ coding interactions.

```{r rq3-chart}
#| label: fig-rq3-chart
#| fig-cap: "Cross-Domain Test Performance (Train: Non-Coding, Test: Coding)"

rq3_df <- data.frame(
  LLM_Family = c("Anthropic (Claude)", "Meta (Llama)", "OpenAI (GPT)"),
  Precision = c(0.61, 0.60, 0.42),
  Recall = c(0.95, 0.38, 0.40),
  F1_Score = c(0.74, 0.46, 0.41)
)

rq3_long <- rq3_df %>%
  pivot_longer(cols = c("Precision", "Recall", "F1_Score"), names_to = "Metric", values_to = "Score")

ggplot(rq3_long, aes(x = LLM_Family, y = Score, fill = Metric)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = c("Precision" = "#16a085", "Recall" = "#f39c12", "F1_Score" = "#2980b9")) +
  scale_y_continuous(limits = c(0, 1.1), labels = scales::percent) +
  labs(title = "RQ3: Cross-Domain Generalization Performance on Coding Prompts",
       subtitle = "Overall Test Accuracy: 55.47%", x = "")
```

$$\text{Cross-Domain Matrix} = \begin{bmatrix} 39 & 0 & 2 \\ 15 & 21 & 20 \\ 10 & 14 & 16 \end{bmatrix}$$

### Domain Shift Insights & Asymmetric Generalization:
1. **Asymmetric Robustness**: The overall accuracy dropped from **63.33%** to **55.47%** under domain shift. However, performance was highly asymmetric across model families.
2. **Claude's Persistent Structural Signature**: Claude achieved a **0.95 recall** (39 out of 41 correct) on unseen coding tasks. This demonstrates that Claude maintains distinct structural habits—such as extensive code explanations, introductory preambles, and post-code summaries—even when generating programming syntax.
3. **Convergence of Llama and GPT Code Style**: Llama's recall dropped significantly to **0.38** (20 misclassified as GPT, 15 as Claude), and GPT's precision dropped to **0.42**. When generating code, both models adopt standard markdown code block formatting (```python), eliminating prose-level stylistic differences and causing the classifier to confuse them.

---

## 4.3 RQ4: Stylistic & Linguistic Feature Analysis

**Research Question 4**: *What structural and linguistic features characterize each LLM family?*

```{r rq4-stylistic-table}
#| label: tbl-rq4
#| tbl-cap: "Empirical Stylistic Metrics Extracted across LLM Families"

ling_df <- data.frame(
  LLM_Family = c("Anthropic (Claude)", "Meta (Llama)", "OpenAI (GPT)"),
  Mean_Chars = c(1075.0, 658.5, 685.4),
  Mean_Words = c(176.6, 108.7, 111.3),
  Markdown_Blocks = c(0.398, 0.230, 0.334),
  Bullet_Points = c(1.886, 0.374, 0.822),
  Type_Token_Ratio = c(0.651, 0.712, 0.732)
)

knitr::kable(ling_df, col.names = c("LLM Family", "Avg Chars", "Avg Words", "Markdown Blocks", "Bullets / Resp", "Type-Token Ratio (TTR)"))
```

```{r rq4-stylistic-plots}
#| label: fig-rq4-charts
#| fig-cap: "Comparison of Linguistic Fingerprints across LLM Families"

p_len <- ggplot(ling_df, aes(x = LLM_Family, y = Mean_Words, fill = LLM_Family)) +
  geom_bar(stat = "identity", width = 0.6) +
  scale_fill_manual(values = llm_colors) +
  labs(title = "Mean Word Count", y = "Words", x = "") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))

p_bullets <- ggplot(ling_df, aes(x = LLM_Family, y = Bullet_Points, fill = LLM_Family)) +
  geom_bar(stat = "identity", width = 0.6) +
  scale_fill_manual(values = llm_colors) +
  labs(title = "Bullet Points / Response", y = "Count", x = "") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))

p_ttr <- ggplot(ling_df, aes(x = LLM_Family, y = Type_Token_Ratio, fill = LLM_Family)) +
  geom_bar(stat = "identity", width = 0.6) +
  scale_fill_manual(values = llm_colors) +
  coord_cartesian(ylim = c(0.5, 0.8)) +
  labs(title = "Lexical Diversity (TTR)", y = "TTR Ratio", x = "") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))

grid.arrange(p_len, p_bullets, p_ttr, ncol = 3)
```

### Mechanistic Explanations of Stylistic Signatures:
1. **Verbosity & RLHF Preference Alignment**: Claude produces responses that are **>60% longer** in character and word count ($\mu = 1,075.0$ chars, $176.6$ words) compared to GPT ($685.4$ chars, $111.3$ words) and Llama ($658.5$ chars, $108.7$ words). This reflects Anthropic's Constitutional AI and RLHF alignment strategies, which penalize abruptness and reward step-by-step reasoning and thorough explanations.
2. **Formatting & Structural Markers**: Claude averages **1.886 bullet points per response**, compared to **0.822** for GPT and **0.374** for Llama. This confirms that the 1D TextCNN heavily leverages markdown delimiters (`- `, `* `, `**`) caught by its $k \in \{3,4,5\}$ n-gram convolution kernels as primary classification signals.
3. **Lexical Diversity & Type-Token Ratio (TTR)**: GPT (**0.732**) and Llama (**0.712**) exhibit significantly higher Type-Token Ratios than Claude (**0.651**). TTR measures vocabulary richness as:

$$\text{TTR} = \frac{|\text{Unique Words}|}{|\text{Total Words}| + 10^{-5}}$$

Because Claude's outputs are much longer, common functional tokens ("the", "and", "to", "is") repeat more frequently, naturally diluting its unique word ratio.

{{< pagebreak >}}

# Section 5: Lessons Learned, Limitations & Future Work

## 5.1 Technical Lessons & Engineering Insights

1. **Dataset Aggregation is Critical**: Fine-grained model variants in crowd-sourced datasets create severe class imbalance. Aggregating models into parent LLM families (Claude, Llama, GPT) was essential for robust learning.
2. **Local N-Gram Features vs. Recurrent States**: TextCNN ($63.33\%$) outperformed BiLSTM ($56.67\%$). LLM fingerprints depend heavily on short structural markers (e.g., bullet delimiters `- `, markdown headers `**`), which CNN parallel kernel windows and max-pooled n-gram filters extract more cleanly than recurrent hidden states.
3. **Prompt Distributional Bias & Leakage**: Prompt-only classification ($51.67\%$) confirmed that benchmark datasets suffer from user selection bias. Evaluating output-only classifiers is necessary to isolate genuine model signatures from user prompt routing bias.
4. **Cross-Domain Resilience**: Stylistic habits like bullet usage and verbose explanations transfer robustly across task domains.
5. **Sequence Length Trade-Offs**: Truncating sequences to 256 tokens captures ~85% of response content while maintaining fast execution on standard CPU hardware.

## 5.2 Limitations & Future Directions

While achieving $63.33\%$ accuracy on a challenging 3-class problem, key limitations offer opportunities for future expansion:

* **Subword Tokenization (BPE/WordPiece)**: Replacing word-level tokenization with byte-pair encoding to handle special code tokens and out-of-vocabulary artifacts.
* **Transformer Fine-Tuning**: Fine-tuning lightweight Transformer backbones or pre-trained embeddings (e.g., DistilBERT, RoBERTa, or DeBERTa) to capture subtle contextual semantics alongside stylometry.
* **Open-Source vs. Proprietary Leakage**: Distillation practices cause open-source models (e.g., Llama fine-tunes) to mimic GPT-4 stylistic habits, compounding classification confusion.
* **Watermarking & Defense Evasion**: Evaluating classifier robustness against paraphrasing attacks or temperature variation remains an open research frontier.
